---
output: 
html_document:
  number_sections=TRUE
pagetitle: Assignment_9
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Assignment 9**

In this assignment, you will use R (within R-Studio) to:
  
+ Load and clean a real data set
+ Conduct exploratory analyses, including informative figures
+ Build and test appropriate models
+ Draw conclusions about your data
+ Combine all of the above into a well-documented R-Markdown report and export (knit) it into an HTML file

**All file paths should be relative, starting from *your* Assignment_9 directory!!**

**This means that you need to create a new R-Project named "Assignment_9.Rproj" in your Assignment_9 directory, and work from scripts within that.**


## **For credit...**

1.  Push a completed version of your Rproj and R-markdown file (details at end of this assignment) to GitHub
2.  Your score will also depend on your analyses and presentation of your final report

____________

# Your tasks:

+ Use the data set "/Data/GradSchool_Admissions.csv"
+ You will explore and model the predictors of graduate school admission
  - the "admit" column is coded as 1=success and 0=failure (that's binary, so model appropriately)
  - the other columns are the GRE score, the GPA, and the rank of the undergraduate institution, where I is "top-tier."
+ Document your data explorations, figures, and conclusions in a reproducible R-markdown report
+ That means I want to see, in your html report, your process of model evaluation and selection. Here's an [example](https://gzahn.github.io/data-course/Repository/Assignments/Assignment_9/example.html){target="_blank"}
+ Upload your **self-contained** R project, including knitted HTML report, to GitHub in *your* Assignment_9 directory

# Analysis

## Data Loading and Cleaning

```{r message=FALSE, warning=FALSE}
# Load
library(tidyverse)

# Read .csv
df <- read.csv("./Data/GradSchool_Admissions.csv")

# Convert admit and rank into factors
df$admit <- as.factor(df$admit)
df$rank <- as.factor(df$rank)

summary(df)

ggplot(df, aes(x = admit, y = gpa, fill = admit)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "GPA vs Graduate Admission",
       x = "Admitted (0 = No, 1 = Yes)",
       y = "Undergraduate GPA")
```

## More Exploring

```{r message=FALSE, warning=FALSE}
# GRE score vs admission
ggplot(df, aes(x = admit, y = gre, fill = admit)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "GRE Score vs Graduate Admission",
       x = "Admitted (0 = No, 1 = Yes)",
       y = "GRE Score")

# Admission rate by institution rank
ggplot(df, aes(x = rank, fill = admit)) +
  geom_bar(position = "fill") +
  theme_minimal() +
  labs(title = "Admission Rate by Undergraduate Institution Rank",
       x = "Institution Rank (1 = Top-tier)",
       y = "Proportion",
       fill = "Admitted")
```

## Model Building

```{r}
model_full <- glm(admit ~ gre + gpa + rank, 
                  data = df, 
                  family = binomial)
summary(model_full)
```

## Model Comparison and Selection

```{r}
# Reduced models to compare against full model
model_no_gre <- glm(admit ~ gpa + rank, data = df, family = binomial)
model_no_gpa <- glm(admit ~ gre + rank, data = df, family = binomial)
model_rank_only <- glm(admit ~ rank, data = df, family = binomial)

# Compare using AIC
AIC(model_full, model_no_gre, model_no_gpa, model_rank_only)

# Compare using likelihood ratio test
anova(model_rank_only, model_no_gre, model_full, test = "Chisq")

# Assign best model
best_model <- model_full
summary(best_model)

# Predicted probability of admission across GPA, split by rank
new_data <- expand.grid(
  gpa  = seq(min(df$gpa), max(df$gpa), length.out = 100),
  gre  = mean(df$gre),
  rank = levels(df$rank)
)

new_data$predicted <- predict(best_model, newdata = new_data, type = "response")

ggplot(new_data, aes(x = gpa, y = predicted, color = rank)) +
  geom_line(linewidth = 1) +
  theme_minimal() +
  labs(title = "Predicted Probability of Admission by GPA and Institution Rank",
       x = "GPA",
       y = "Predicted Probability of Admission",
       color = "Inst. Rank")
```

## Conclusions
- If all other variables are constant, increasing your GPA by one unit/ point increases your odds of admission to grad school by about 2.23 times. 

```{r message=FALSE, warning=FALSE}
# Summary of admission rates
df %>%
  group_by(rank, admit) %>%
  summarise(n = n(), .groups = "drop") %>%
  pivot_wider(names_from = admit, values_from = n, names_prefix = "admit_") %>%
  mutate(admission_rate = admit_1 / (admit_0 + admit_1))

# Odds ratios with confidence intervals
exp(coef(best_model))
exp(confint(best_model))
```