---
title: "Exam 3"
author: "Isaac Chamberlain"
date: "10797985"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(broom)
```

```{r}
salary_data <- read.csv("FacultySalaries_1995.csv")
juniper_data <- read.csv("Juniper_Oils.csv")
```

```{r, warning=FALSE}
# 1
salary_long <- salary_data %>%
  pivot_longer(cols = c("AvgAssistProfSalary", "AvgAssocProfSalary", "AvgFullProfSalary"), 
               names_to = "Rank", 
               values_to = "Salary") %>%
  # "VIIB" was being shown as a fourth dataset, but it seemed like it was just empty. It wasn't shown in the instructions, so I removed it here. 
  filter(!is.na(Tier) & Tier != "" & Tier != "VIIB") %>% 
  mutate(Rank = recode(Rank, 
                       "AvgAssistProfSalary" = "Assist", 
                       "AvgAssocProfSalary" = "Assoc", 
                       "AvgFullProfSalary" = "Full"),
         Rank = factor(Rank, levels = c("Assist", "Assoc", "Full"))) %>%
  drop_na(Salary)

ggplot(salary_long, aes(x = Rank, y = Salary, fill = Rank)) +
  geom_boxplot() +
  facet_wrap(~Tier, nrow = 1) +
  theme_minimal()
```

```{r}
# 2
salary_model <- aov(Salary ~ State + Tier + Rank, data = salary_long)
summary(salary_model)
```

```{r}
# 3
chemical_names <- c("alpha.pinene","para.cymene","alpha.terpineol","cedr.9.ene","alpha.cedrene","beta.cedrene","cis.thujopsene","alpha.himachalene","beta.chamigrene","cuparene","compound.1","alpha.chamigrene","widdrol","cedrol","beta.acorenol","alpha.acorenol","gamma.eudesmol","beta.eudesmol","alpha.eudesmol","cedr.8.en.13.ol","cedr.8.en.15.ol","compound.2","thujopsenal")

juniper_long <- juniper_data %>%
  pivot_longer(cols = all_of(chemical_names), 
               names_to = "ChemicalID", 
               values_to = "Concentration")
```

```{r}
# 4
```{r, message=FALSE, warning=FALSE}
ggplot(juniper_long, aes(x = YearsSinceBurn, y = Concentration)) +
  geom_smooth(method = "loess", se = TRUE, color = "blue", fill = "lightblue") +
  facet_wrap(~ChemicalID, scales = "free_y") +
  theme_bw() +
  theme(
    strip.background = element_rect(fill = "white", color = "white"),
    strip.text = element_text(size = 8, color = "black")
  )
```

```{r, message=FALSE, warning=FALSE}
# 5
juniper_glm <- glm(Concentration ~ YearsSinceBurn * ChemicalID, data = juniper_long)

juniper_results <- tidy(juniper_glm) %>%
  filter(p.value < 0.05) %>%
  mutate(term = str_remove(term, "ChemicalID"),
         term = str_replace_all(term, "\\.", "-"))

print(juniper_results)
```