---
title: "BIOL 3100 Final Project"
author: "Isaac Chamberlain"
output:
  html_document:
    self_contained: true
    theme: flatly
    toc: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(scipen = 999)
```

```{r packages, include=FALSE}
library(tidyverse)
library(lubridate)
library(plotly)
library(htmltools)
library(jsonlite)
```

```{r data-prep, include=FALSE}
patient_file <- "Fake Patient Info.csv"
appointment_file <- "Fake Appointment Info.csv"

patients_raw <- read.csv(patient_file, check.names = FALSE, stringsAsFactors = FALSE)
appointments_raw <- read.csv(appointment_file, check.names = FALSE, stringsAsFactors = FALSE)

patients <- patients_raw %>%
  mutate(
    patient_name = str_trim(paste(`First Name`, `Last Name`)),
    birth_date = suppressWarnings(mdy(`Birth Date`)),
    patient_status = na_if(Status, ""),
    birth_gender = na_if(`Birth Gender`, ""),
    referring_provider = na_if(`Referring Provider`, "")
  )

appointments <- appointments_raw %>%
  mutate(
    appointment_datetime = suppressWarnings(mdy_hm(`Appt Date`)),
    appointment_date = as.Date(appointment_datetime),
    provider = factor(Provider, levels = sort(unique(Provider))),
    provider_label = paste("Provider", provider),
    appointment_status = na_if(Status, ""),
    visit_type = na_if(Summary, ""),
    patient_name = str_trim(`Patient Name`),
    seen_flag = str_detect(
      str_to_lower(coalesce(appointment_status, "")),
      "checked in|payment complete|pt conf"
    ),
    new_patient_flag = str_detect(str_to_lower(coalesce(visit_type, "")), "new patient")
  ) %>%
  left_join(
    patients %>%
      select(patient_name, Age = `Age(yrs)`, patient_status, birth_gender, referring_provider),
    by = "patient_name"
  ) %>%
  filter(!is.na(appointment_date)) %>%
  mutate(
    appointment_status = coalesce(appointment_status, "Unknown"),
    visit_type = coalesce(visit_type, "Unknown"),
    referring_provider = coalesce(referring_provider, "Unknown")
  )

provider_choices <- sort(unique(as.character(appointments$provider_label)))

dashboard_data <- appointments %>%
  transmute(
    patient_name,
    appointment_date = format(appointment_date, "%Y-%m-%d"),
    provider_label,
    appointment_status,
    visit_type,
    seen_flag,
    new_patient_flag,
    referring_provider
  )

dashboard_json <- jsonlite::toJSON(
  dashboard_data,
  dataframe = "rows",
  auto_unbox = TRUE,
  na = "null"
)

min_date_text <- paste(month(min(appointments$appointment_date)), day(min(appointments$appointment_date)), format(min(appointments$appointment_date), "%y"), sep = "-")
max_date_text <- paste(month(max(appointments$appointment_date)), day(max(appointments$appointment_date)), format(max(appointments$appointment_date), "%y"), sep = "-")

dashboard_css <- "
body {
  font-size: 16px;
}
.container-fluid {
  max-width: 1380px;
}
h1.title {
  font-size: 2.4rem;
  margin-bottom: 0.2em;
}
h1, h2 {
  line-height: 1.15;
}
.dashboard-title {
  margin: 0 0 14px 0;
}
.dashboard-layout {
  display: flex;
  gap: 22px;
  align-items: flex-start;
}
.dashboard-sidebar {
  width: 280px;
  flex: 0 0 280px;
  border: none;
  border-radius: 16px;
  background: #f4f7fb;
  box-shadow: 0 8px 20px rgba(25, 55, 85, 0.08);
  padding: 18px 18px 12px 18px;
}
.dashboard-main {
  flex: 1 1 auto;
  min-width: 0;
}
.control-group {
  margin-bottom: 18px;
}
.control-label {
  display: block;
  font-weight: 700;
  margin-bottom: 8px;
  color: #2c3e50;
}
.form-control-staticish,
.dashboard-sidebar select,
.dashboard-sidebar input[type='text'] {
  width: 100%;
  border: 2px solid #d7e3f0;
  border-radius: 10px;
  padding: 10px 12px;
  background: #fff;
}
.date-row {
  display: grid;
  grid-template-columns: 1fr 1fr;
  gap: 10px;
}
.radio-stack {
  display: grid;
  gap: 6px;
}
.radio-stack label {
  font-weight: 400;
  margin: 0;
}
.forecast-endpoints {
  display: flex;
  justify-content: space-between;
  font-size: 12px;
  color: #5a6d80;
  margin-bottom: 4px;
}
.forecast-range {
  width: 100%;
  margin-bottom: 2px;
}
.forecast-readout {
  font-size: 13px;
  color: #5a6d80;
  margin-top: 6px;
}
.tick-track {
  display: grid;
  grid-template-columns: repeat(12, 1fr);
  gap: 0;
  margin-top: 2px;
}
.tick-track span {
  display: block;
  height: 8px;
  border-left: 1px solid #9aa9b7;
}
.tick-track span:last-child {
  border-right: 1px solid #9aa9b7;
}
.help-note {
  font-size: 13px;
  color: #5a6d80;
  line-height: 1.4;
}
.metric-card {
  background: linear-gradient(180deg, #ffffff 0%, #f8fbff 100%);
  border: 1px solid #d7e3f0;
  border-radius: 16px;
  padding: 14px 16px;
  min-height: 112px;
  box-shadow: 0 8px 18px rgba(25, 55, 85, 0.08);
  margin-bottom: 14px;
}
.metric-card h4 {
  margin-top: 0;
  margin-bottom: 6px;
  font-size: 15px;
  text-transform: uppercase;
  letter-spacing: 0.04em;
  color: #4b6278;
}
.metric-value {
  font-size: 24px;
  font-weight: 700;
  color: #20364d;
  line-height: 1.15;
  overflow-wrap: anywhere;
}
.chart-panel {
  background: #ffffff;
  border: 1px solid #d7e3f0;
  border-radius: 16px;
  padding: 10px 12px 4px 12px;
  margin-bottom: 16px;
  box-shadow: 0 8px 18px rgba(25, 55, 85, 0.08);
}
.chart-box {
  width: 100%;
  height: 320px;
}
.summary-table-wrap {
  overflow-x: auto;
}
.summary-table {
  width: 100%;
  border-collapse: collapse;
}
.summary-table th,
.summary-table td {
  padding: 10px 12px;
  border-bottom: 1px solid #e6edf5;
  text-align: left;
  vertical-align: top;
}
.summary-table th {
  font-size: 13px;
  text-transform: uppercase;
  letter-spacing: 0.04em;
  color: #4b6278;
}
.summary-table td {
  color: #20364d;
}
.nav-tabs {
  margin-bottom: 14px;
}
.nav-tabs > li > a {
  border-radius: 10px 10px 0 0;
  font-weight: 600;
}
@media (max-width: 991px) {
  .dashboard-layout {
    flex-direction: column;
  }
  .dashboard-sidebar {
    width: 100%;
    flex-basis: auto;
  }
}
"

dashboard_js <- "
function parseMDY(value) {
  const match = String(value || '').trim().match(/^(\\d{1,2})-(\\d{1,2})-(\\d{2})$/);
  if (!match) return null;
  const month = Number(match[1]);
  const day = Number(match[2]);
  const year = 2000 + Number(match[3]);
  const date = new Date(year, month - 1, day);
  if (date.getFullYear() !== year || date.getMonth() !== month - 1 || date.getDate() !== day) {
    return null;
  }
  return date;
}

function parseISODate(value) {
  return new Date(value + 'T00:00:00');
}

function formatMDY(date) {
  const yy = String(date.getFullYear()).slice(-2);
  return `${date.getMonth() + 1}-${date.getDate()}-${yy}`;
}

function comma(value) {
  return new Intl.NumberFormat('en-US', { maximumFractionDigits: 0 }).format(value);
}

function percent(value) {
  return `${(value * 100).toFixed(1)}%`;
}

function monthKey(date) {
  return `${date.getFullYear()}-${String(date.getMonth() + 1).padStart(2, '0')}`;
}

function monthLabel(date) {
  return date.toLocaleDateString('en-US', { month: 'short', year: 'numeric' });
}

function wrapText(value, width) {
  if (!value) return '';
  const words = String(value).split(/\\s+/);
  const lines = [];
  let current = '';
  words.forEach(word => {
    const test = current ? `${current} ${word}` : word;
    if (test.length > width && current) {
      lines.push(current);
      current = word;
    } else {
      current = test;
    }
  });
  if (current) lines.push(current);
  return lines.join('<br>');
}

function topWithOthers(records, accessor, n) {
  const counts = new Map();
  records.forEach(record => {
    const key = accessor(record) || 'Unknown';
    counts.set(key, (counts.get(key) || 0) + 1);
  });
  const sorted = Array.from(counts.entries()).sort((a, b) => b[1] - a[1]);
  const top = sorted.slice(0, n).map(([label, count]) => ({ label, count }));
  const remainder = sorted.slice(n).reduce((sum, item) => sum + item[1], 0);
  if (remainder > 0) top.push({ label: 'Other', count: remainder });
  return top;
}

function getMonthlyActual(records) {
  const counts = new Map();
  records.forEach(record => {
    const date = parseISODate(record.appointment_date);
    const first = new Date(date.getFullYear(), date.getMonth(), 1);
    const key = monthKey(first);
    counts.set(key, (counts.get(key) || 0) + 1);
  });
  return Array.from(counts.entries())
    .sort((a, b) => a[0].localeCompare(b[0]))
    .map(([key, appointments]) => {
      const [year, month] = key.split('-').map(Number);
      return { month: new Date(year, month - 1, 1), appointments };
    });
}

function getMonthlyForecast(actual, months) {
  if (actual.length < 3) return [];
  const xs = actual.map((_, i) => i + 1);
  const ys = actual.map(item => item.appointments);
  const xMean = xs.reduce((a, b) => a + b, 0) / xs.length;
  const yMean = ys.reduce((a, b) => a + b, 0) / ys.length;
  let numerator = 0;
  let denominator = 0;
  for (let i = 0; i < xs.length; i += 1) {
    numerator += (xs[i] - xMean) * (ys[i] - yMean);
    denominator += (xs[i] - xMean) ** 2;
  }
  const slope = denominator === 0 ? 0 : numerator / denominator;
  const intercept = yMean - slope * xMean;
  const lastMonth = actual[actual.length - 1].month;
  const forecast = [];
  for (let i = 1; i <= months; i += 1) {
    const monthIndex = actual.length + i;
    const date = new Date(lastMonth.getFullYear(), lastMonth.getMonth() + i, 1);
    const prediction = Math.max(0, intercept + slope * monthIndex);
    forecast.push({ month: date, appointments: prediction });
  }
  return forecast;
}

function mostCommonVisit(records) {
  const counts = new Map();
  records.forEach(record => {
    const key = record.visit_type || 'Unknown';
    counts.set(key, (counts.get(key) || 0) + 1);
  });
  const sorted = Array.from(counts.entries()).sort((a, b) => b[1] - a[1]);
  return sorted.length ? sorted[0][0] : 'N/A';
}

function getFilteredRecords() {
  const provider = document.getElementById('provider_select').value;
  const startInput = document.getElementById('start_date').value;
  const endInput = document.getElementById('end_date').value;
  const startDate = parseMDY(startInput);
  const endDate = parseMDY(endInput);
  if (!startDate || !endDate || startDate > endDate) return [];
  return rawAppointments.filter(record => {
    const date = parseISODate(record.appointment_date);
    const providerMatch = provider === 'All Providers' || record.provider_label === provider;
    return providerMatch && date >= startDate && date <= endDate;
  });
}

function renderMetrics(records) {
  const total = records.length;
  const uniquePatients = new Set(records.map(record => record.patient_name)).size;
  const seen = records.filter(record => record.seen_flag).length;
  const newPatients = records.filter(record => record.new_patient_flag);
  const newSeen = newPatients.filter(record => record.seen_flag).length;
  document.getElementById('metric_total_appointments').textContent = comma(total);
  document.getElementById('metric_unique_patients').textContent = comma(uniquePatients);
  document.getElementById('metric_show_rate').textContent = total ? percent(seen / total) : 'N/A';
  document.getElementById('metric_new_scheduled').textContent = comma(newPatients.length);
  document.getElementById('metric_new_seen').textContent = comma(newSeen);
  document.getElementById('metric_new_show_rate').textContent = newPatients.length ? percent(newSeen / newPatients.length) : 'N/A';
}

function renderMonthlyPlot(records) {
  const actual = getMonthlyActual(records);
  const forecastMonths = Number(document.getElementById('forecast_months').value);
  const trendMode = document.querySelector('input[name=\"trend_mode\"]:checked').value;
  const forecast = getMonthlyForecast(actual, forecastMonths);
  const traces = [];

  if ((trendMode === 'actual' || trendMode === 'both') && actual.length) {
    traces.push({
      x: actual.map(item => item.month),
      y: actual.map(item => item.appointments),
      type: 'scatter',
      mode: 'lines+markers',
      name: 'Actual',
      line: { color: '#1b6ca8', width: 3 },
      marker: { size: 7, color: '#1b6ca8' },
      hovertemplate: 'Month: %{x|%b %Y}<br>Appointments: %{y:,}<extra></extra>'
    });
  }

  if ((trendMode === 'forecast' || trendMode === 'both') && forecast.length) {
    traces.push({
      x: forecast.map(item => item.month),
      y: forecast.map(item => item.appointments),
      type: 'scatter',
      mode: 'lines+markers',
      name: 'Forecast',
      line: { color: '#d95f02', width: 3, dash: 'dash' },
      marker: { size: 7, color: '#d95f02' },
      hovertemplate: 'Forecast month: %{x|%b %Y}<br>Predicted appointments: %{y:,.0f}<extra></extra>'
    });
  }

  Plotly.newPlot('monthly_trend_plot', traces, {
    title: { text: '<b>Monthly Appointment Volume</b>' },
    margin: { l: 70, r: 20, t: 55, b: 55 },
    paper_bgcolor: '#ffffff',
    plot_bgcolor: '#ffffff',
    hoverlabel: { align: 'left' },
    xaxis: { title: '', tickformat: '%b\\n%Y' },
    yaxis: { title: 'Appointments', tickformat: ',d' },
    legend: { orientation: 'h', x: 0, y: 1.12 }
  }, { displayModeBar: false, responsive: true });
}

function renderStatusPlot(records) {
  const statusCounts = topWithOthers(records, record => record.appointment_status, 6);
  Plotly.newPlot('status_plot', [{
    type: 'bar',
    orientation: 'h',
    x: statusCounts.map(item => item.count).reverse(),
    y: statusCounts.map(item => wrapText(item.label, 18)).reverse(),
    marker: { color: ['#6baed6', '#74c476', '#fd8d3c', '#9e9ac8', '#fdae6b', '#9ecae1', '#bdbdbd'].slice(0, statusCounts.length).reverse() },
    hovertemplate: statusCounts.map(item => `Status: ${item.label}<br>Appointments: ${comma(item.count)}<extra></extra>`).reverse()
  }], {
    title: { text: '<b>Appointment Status Distribution</b>' },
    margin: { l: 130, r: 20, t: 55, b: 30 },
    paper_bgcolor: '#ffffff',
    plot_bgcolor: '#ffffff',
    showlegend: false,
    xaxis: { title: 'Number of Appointments', tickformat: ',d' },
    yaxis: { automargin: true }
  }, { displayModeBar: false, responsive: true });
}

function renderWeekdayPlot(records) {
  const weekdays = ['Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday'];
  const counts = new Map(weekdays.map(day => [day, 0]));
  records.forEach(record => {
    const day = parseISODate(record.appointment_date).toLocaleDateString('en-US', { weekday: 'long' });
    if (counts.has(day)) counts.set(day, counts.get(day) + 1);
  });
  Plotly.newPlot('weekday_plot', [{
    type: 'scatter',
    mode: 'lines+markers',
    x: weekdays,
    y: weekdays.map(day => counts.get(day)),
    line: { color: '#2a9d8f', width: 3 },
    marker: { size: 7, color: '#2a9d8f' },
    hovertemplate: weekdays.map(day => `Day: ${day}<br>Appointments: ${comma(counts.get(day))}<extra></extra>`)
  }], {
    title: { text: '<b>Appointments by Day of Week</b>' },
    margin: { l: 60, r: 20, t: 55, b: 50 },
    paper_bgcolor: '#ffffff',
    plot_bgcolor: '#ffffff',
    xaxis: { title: '' },
    yaxis: { title: 'Number of Appointments', tickformat: ',d' }
  }, { displayModeBar: false, responsive: true });
}

function renderReferralPlot(records) {
  const referralCounts = topWithOthers(records.filter(record => record.referring_provider), record => record.referring_provider, 6);
  Plotly.newPlot('referral_plot', [{
    type: 'bar',
    orientation: 'h',
    x: referralCounts.map(item => item.count).reverse(),
    y: referralCounts.map(item => wrapText(item.label, 18)).reverse(),
    marker: { color: ['#5dade2', '#48c9b0', '#f5b041', '#af7ac5', '#ec7063', '#7fb3d5', '#bdbdbd'].slice(0, referralCounts.length).reverse() },
    hovertemplate: referralCounts.map(item => `Referral source: ${item.label}<br>Patients: ${comma(item.count)}<extra></extra>`).reverse()
  }], {
    title: { text: '<b>Referrals from Each Source</b>' },
    margin: { l: 135, r: 20, t: 55, b: 30 },
    paper_bgcolor: '#ffffff',
    plot_bgcolor: '#ffffff',
    showlegend: false,
    xaxis: { title: 'Number of Patients', tickformat: ',d' },
    yaxis: { automargin: true }
  }, { displayModeBar: false, responsive: true });
}

function renderSummaryTable(records) {
  const providerSelection = document.getElementById('provider_select').value;
  const providers = providerSelection === 'All Providers'
    ? Array.from(new Set(records.map(record => record.provider_label))).sort()
    : [providerSelection];

  const rows = providers.map(provider => {
    const providerRecords = records.filter(record => record.provider_label === provider);
    const seen = providerRecords.filter(record => record.seen_flag).length;
    const newPatients = providerRecords.filter(record => record.new_patient_flag).length;
    return {
      provider,
      appointments: providerRecords.length,
      uniquePatients: new Set(providerRecords.map(record => record.patient_name)).size,
      showRate: providerRecords.length ? percent(seen / providerRecords.length) : 'N/A',
      newPatients,
      commonVisit: mostCommonVisit(providerRecords)
    };
  }).sort((a, b) => b.appointments - a.appointments);

  const tbody = document.getElementById('summary_table_body');
  tbody.innerHTML = rows.map(row => `
    <tr>
      <td>${row.provider}</td>
      <td>${comma(row.appointments)}</td>
      <td>${comma(row.uniquePatients)}</td>
      <td>${row.showRate}</td>
      <td>${comma(row.newPatients)}</td>
      <td>${row.commonVisit}</td>
    </tr>
  `).join('');
}

function updateDashboard() {
  const records = getFilteredRecords();
  document.getElementById('forecast_readout').textContent = `${document.getElementById('forecast_months').value} month forecast`;
  renderMetrics(records);
  renderMonthlyPlot(records);
  renderStatusPlot(records);
  renderWeekdayPlot(records);
  renderReferralPlot(records);
  renderSummaryTable(records);
}

document.addEventListener('DOMContentLoaded', function () {
  document.getElementById('provider_select').addEventListener('change', updateDashboard);
  document.getElementById('start_date').addEventListener('change', updateDashboard);
  document.getElementById('end_date').addEventListener('change', updateDashboard);
  document.getElementById('forecast_months').addEventListener('input', updateDashboard);
  document.querySelectorAll('input[name=\"trend_mode\"]').forEach(input => {
    input.addEventListener('change', updateDashboard);
  });
  updateDashboard();
});
"
```

# Interactive Dashboard

This dashboard is my final project. It allows me to see different statistics for our clinic as a whole, or for individual providers, during a specified date range. There is also a feature that runs a simple prediction for the number of patients we will be seeing per month up to 12 months in the future.

This dashboard is based on data I use at work to track the performance of our family medicine clinic. The data used for this project follows the same structure as the data I use at work (same column names and number of columns), but all protected health information was removed and replaced with fake data for patient privacy. These are the two `.csv` files that were used for this dashboard:

- `Fake Patient Info.csv`: patient information such as age, status (active, lead, etc.), gender, and referral source.
- `Fake Appointment Info.csv`: appointment information such as provider, appointment date, visit summary, and appointment status.

This, among other data, is important to monitor as we make process changes. It can tell us if our changes are making any difference, and if that difference is positive or negative. It can also help us predict where we will be in the future so we can plan for future hires and other expenses.

```{r dashboard-page, echo=FALSE}
dashboard_page <- htmltools::tagList(
  plotly:::plotlyMainBundle(),
  tags$style(HTML(dashboard_css)),
  div(
    class = "dashboard-title",
    h3("Clinic Operations Dashboard")
  ),
  div(
    class = "dashboard-layout",
    div(
      class = "dashboard-sidebar",
      div(
        class = "control-group",
        tags$label(class = "control-label", `for` = "provider_select", "Provider view"),
        tags$select(
          id = "provider_select",
          class = "form-control-staticish",
          lapply(c("All Providers", provider_choices), function(choice) {
            tags$option(value = choice, choice)
          })
        )
      ),
      div(
        class = "control-group",
        tags$label(class = "control-label", "Appointment date range"),
        div(
          class = "date-row",
          tags$input(id = "start_date", type = "text", value = min_date_text, placeholder = "M-D-YY"),
          tags$input(id = "end_date", type = "text", value = max_date_text, placeholder = "M-D-YY")
        )
      ),
      div(
        class = "control-group",
        tags$label(class = "control-label", "Trend display"),
        div(
          class = "radio-stack",
          tags$label(tags$input(type = "radio", name = "trend_mode", value = "actual", checked = NA), " Actual only"),
          tags$label(tags$input(type = "radio", name = "trend_mode", value = "forecast"), " Forecast only"),
          tags$label(tags$input(type = "radio", name = "trend_mode", value = "both"), " Actual + Forecast")
        )
      ),
      div(
        class = "control-group",
        tags$label(class = "control-label", `for` = "forecast_months", "Months to forecast"),
        div(class = "forecast-endpoints", span("1"), span("12")),
        tags$input(id = "forecast_months", class = "forecast-range", type = "range", min = "1", max = "12", value = "3", step = "1"),
        div(class = "tick-track", lapply(seq_len(12), function(i) tags$span())),
        div(id = "forecast_readout", class = "forecast-readout", "3 month forecast")
      ),
      div(
        class = "help-note",
        "Use these controls to compare the entire clinic with a single provider and to view a simple short-term forecast based on past monthly volume."
      )
    ),
    div(
      class = "dashboard-main",
      tags$ul(
        class = "nav nav-tabs",
        role = "tablist",
        tags$li(class = "active", role = "presentation", tags$a(href = "#overview_tab", `data-toggle` = "tab", "Overview")),
        tags$li(role = "presentation", tags$a(href = "#patterns_tab", `data-toggle` = "tab", "Patterns"))
      ),
      div(
        class = "tab-content",
        div(
          id = "overview_tab",
          class = "tab-pane fade in active",
          div(
            class = "row",
            div(class = "col-sm-4", div(class = "metric-card", h4("Appointments"), div(id = "metric_total_appointments", class = "metric-value"))),
            div(class = "col-sm-4", div(class = "metric-card", h4("Unique Patients"), div(id = "metric_unique_patients", class = "metric-value"))),
            div(class = "col-sm-4", div(class = "metric-card", h4("Show Rate"), div(id = "metric_show_rate", class = "metric-value")))
          ),
          div(
            class = "row",
            div(class = "col-sm-4", div(class = "metric-card", h4("New Patients Scheduled"), div(id = "metric_new_scheduled", class = "metric-value"))),
            div(class = "col-sm-4", div(class = "metric-card", h4("New Patients Seen"), div(id = "metric_new_seen", class = "metric-value"))),
            div(class = "col-sm-4", div(class = "metric-card", h4("New Patient Show Rate"), div(id = "metric_new_show_rate", class = "metric-value")))
          ),
          div(class = "chart-panel", div(id = "monthly_trend_plot", class = "chart-box")),
          div(class = "chart-panel", div(id = "status_plot", class = "chart-box"))
        ),
        div(
          id = "patterns_tab",
          class = "tab-pane fade",
          div(class = "chart-panel", div(id = "weekday_plot", class = "chart-box")),
          div(class = "chart-panel", div(id = "referral_plot", class = "chart-box")),
          div(
            class = "chart-panel summary-table-wrap",
            tags$table(
              class = "summary-table",
              tags$thead(
                tags$tr(
                  tags$th("Provider"),
                  tags$th("Appointments"),
                  tags$th("Unique Patients"),
                  tags$th("Show Rate"),
                  tags$th("New Patients"),
                  tags$th("Most Common Visit Type")
                )
              ),
              tags$tbody(id = "summary_table_body")
            )
          )
        )
      )
    )
  ),
  tags$script(HTML(paste0("const rawAppointments = ", dashboard_json, ";\n", dashboard_js)))
)

htmltools::browsable(dashboard_page)
```
